Kyoto VR MQP Paper First Draft

### 2019-09-26 paper.tex
fix grammar

Viro AR comes in two flavors: ViroReact and ViroCore. ViroCore allows
developers to build an AR Application with Java. The disadvantage of this is
that ViroCore only allows developers to target Android, which unfortunately
made ViroCore not an option for our project. ViroReact is the cross-platform
option for ViroAR. ViroReact leverages the cross-platform capabilities of
React, which is Facebook's Javascript Library for developing user
interfaces~\autocite{facebook2019}.

@@

@@

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps \autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience.
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project.

@@

In order to test for bugs, all three of us periodically interacted with
successive builds of the frontend. When bugs were found, we would log these as
``Issues'' on the GitHub repo. These issues would get resolved in successive
pull requests.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to
test the GPS functionality of the app, we used Editour to design an example
tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
us to catch various bugs before we created a finalized prototype for
field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
what we used for testing the app. The ``C-Shaped Region'' helped us test
concave regions. This uniquely shaped region also prompted us to think about
what UI behavior made the most sense if a user were to walk into a region, walk
out and then in again. We decided that it was awkward if the audio restarted
upon re-entering a region, since the audio would still be playing once a user
left the region. The region at the bottom surrounding our domitories was added
for our convenience, allowing us to test the app while we were away from the
lab.  As we began to implement more complex UI that changed based on GPS
position in various ways, directly taking the tour by walking around was an
invaluable way to test. Section~\ref{sec:adobeXdDesign} details how the UI grew
in complexity in the late stages of the project. Having a way to regularly run
field tests was integral to polishing the app in time before we revisited
Kinkaku-ji.  Because the Editour was flexible enough to easily swap out media
and add regions to the tour, the Editour proved itself to be as helpful for
testing as it was for crafting the final tour that could be taken at
Kinkaku-ji.

@@

Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji}
to create a second, ``chunkier'' tour.  In the tour-file
\texttt{kinkakuji-chunkier}, we expanded all of the regions to accomodate for
potential GPS inaccuracies that could place the user outside the range of the
audio-trigger region.  Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour
that we used for field testing at Kinkaku-ji.

@@

\appendices
\section{Editour API Documentation}

>>>>

Viro AR comes in two flavors: ViroReact and ViroCore. ViroCore allows
developers to build an AR Application with Java. The disadvantage of this is
that ViroCore only allows developers to target Android, which unfortunately
made ViroCore not an option for our project. ViroReact is the cross-platform
option for ViroAR. ViroReact leverages the cross-platform capabilities of
React, which is Facebook's JavaScript Library for developing user
interfaces~\autocite{facebook2019}.

@@

The backend implements a representational state transfer (REST) API, utilizing
HTTP methods to manipulate tour data on the server. For full documentation of
the backend's API, see Appendix~\ref{sec:editourAPIDocumentation}.

@@

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps~\autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience.
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project.

@@

In order to test for bugs, all three of us periodically interacted with
successive builds of the frontend. When bugs were found, we would log these as
``Issues'' on the GitHub repository. These issues would get resolved in
successive pull requests.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to
test the GPS functionality of the app, we used Editour to design an example
tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
us to catch various bugs before we created a finalized prototype for
field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
what we used for testing the app. The ``C-Shaped Region'' helped us test
concave regions. This uniquely shaped region also prompted us to think about
what UI behavior made the most sense if a user were to walk into a region, walk
out and then in again. We decided that it was awkward if the audio restarted
upon re-entering a region, since the audio would still be playing once a user
left the region. The region at the bottom surrounding our dormitories was added
for our convenience, allowing us to test the app while we were away from the
lab.  As we began to implement more complex UI that changed based on GPS
position in various ways, directly taking the tour by walking around was an
invaluable way to test. Section~\ref{sec:adobeXdDesign} details how the UI grew
in complexity in the late stages of the project. Having a way to regularly run
field tests was integral to polishing the app in time before we revisited
Kinkaku-ji.  Because the Editour was flexible enough to easily swap out media
and add regions to the tour, the Editour proved itself to be as helpful for
testing as it was for crafting the final tour that could be taken at
Kinkaku-ji.

@@

Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji}
to create a second, ``chunkier'' tour.  In the tour-file
\texttt{kinkakuji-chunkier}, we expanded all of the regions to accommodate for
potential GPS inaccuracies that could place the user outside the range of the
audio-trigger region.  Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour
that we used for field testing at Kinkaku-ji.

@@

\appendices
\section{Editour API Documentation}
\label{sec:editourAPIDocumentation}
